\subsection{Influence of Implementations}
\label{subsec:experiments-implementations}

We discuss the influence of implementation details on performance and runtime for
different implementations of \SEEDS, \SLIC and \FH. In particular, \reSEEDS and \reFH 
are our revised implementations of \SEEDS and \FH, respectively. 
Both implementations follow the algorithm as described in the corresponding publications,
provide exactly the same parameters and are also implemented in C/C++.
Still, we tried to optimize the implementations with respect to connectivity and
kept them as efficient as possible. 
\reFH additionally uses a slightly different graph data structure -- we refer to the
implementations for details; these will be made publicly available together with the benchmark.
Furthermore, we include \vlSLIC, an implementation of \SLIC as part of the VLFeat library
\cite{VedaldiFulkerson:2008}, and \preSLIC \cite{NeubertProtzel:2014}, an accelerated version of \SLIC based on the
original implementation. Both \vlSLIC and \preSLIC are also implemented in C/C++ as
their original counterparts.

We find that revisiting implementation details may be beneficial for both performance and runtime.
We consider Figure \ref{fig:experiments-implementations-bsds500} showing \Rec, \UE
and runtime in seconds $t$ for the introduced implementations of \SLIC, \SEEDS and \FH on the \BSDS dataset.
For \reSEEDSr and \reFHr, we observe improved performance which can be related to
the improved connectivity. However, even very similar implementations such as \SLICr
and \vlSLICr differ slightly in performance; note the lower \Rec and higher \UE
of \vlSLICr compared to \SLICr. Overall, the difference in runtime is most striking, for example \reSEEDSr
and \preSLICr show significantly lower runtime compared to \SEEDSr and \SLICr.
\reFHr, in contrast, shows higher runtime compared to \FHr due to a more complex data structure.
%We conclude that revisiting implementation details may improve performance and reduce runtime.

As expected, implementation details effect runtime, however, in the presented cases,
\ie for \SLIC, \SEEDS and \FH, performance is also affected. Nevertheless, it
still needs to be examined whether this holds true for the remaining algorithms, as well.
Furthermore, the experiments suggest that improving connectivity helps
performance.
